Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/introduction.tex
small typo

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, \citet{Kakade-Shalev-Shwartz-Tewari-2008} ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}

>>>>

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, \citet{Kakade-Shalev-Shwartz-Tewari-2008} ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}
